### 2021-06-21 src/paper/model/testing.tex

To distribute the correct number of PCR tests among symptomatic and asymptomatic
infections without knowing explicit test demand probabilities, we use the following
approach: First, we calculate the total number of positive PCR tests by multiplying the
number of newly infected individuals with an estimate of the share of detected cases from
the Dunkelzifferradar project. \footnote{The Dunkelzifferradar project publishes daily
estimates of the dark figure of infections under
\url{https://covid19.dunkelzifferradar.de/}} Next, we determine how many of these tests
should go to symptomatic and asymptomatic individuals from data by the Robert Koch
Institut.\comment[id=J]{add source} Then, we sample the individuals to which those tests
are allocated from the pools of symptomatic and asyptomatic infected but not yet tested
individuals.

Sampling uniformly from the pool of symptomatic individuals ensures that age groups who
are more likely to develop symptoms are also more likely to receive tests. Thus, the
share of detected cases is much higher for the elderly than for children in time periods
where many tests are done because of symptoms which is in line with the estimates from
the literature.\comment[id=J]{need source}

>>>>

To distribute the correct number of PCR tests among symptomatic and asymptomatic
infections without knowing explicit test demand probabilities, we use the following
approach: First, we calculate the total number of positive PCR tests by multiplying the
number of newly infected individuals with an estimate of the share of detected cases from
the Dunkelzifferradar project. \footnote{The Dunkelzifferradar project publishes daily
estimates of the dark figure of infections under
\url{https://covid19.dunkelzifferradar.de/}} Next, we determine how many of these tests
should go to symptomatic and asymptomatic individuals from data by the Robert Koch
Institut. \comment[id=J]{add source}
Then, we sample the individuals to which those tests are allocated from the pools of
symptomatic and asyptomatic infected but not yet tested individuals.

Sampling uniformly from the pool of symptomatic individuals ensures that age groups who
are more likely to develop symptoms are also more likely to receive tests. Thus, the
share of detected cases is much higher for the elderly than for children in time periods
where many tests are done because of symptoms which is in line with the estimates from
the literature. \comment[id=J]{need source}
